Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-06 paper_jasa.tex
visual versus classical curves
results

Under the null hypothesis $X \sim Binom_{K, 1/m}$, leading to a power of 
\[
\text{Power}_V(\theta, K)= 1 - Binom_{K, 11/m} (x_\alpha - 1),
\]
where $x_\alpha$ is defined as in (\ref{dfn:test}), as  $P(X \ge x_{\alpha}) < \alpha$.

@@

Let $X_{\ell i} \sim Binom_{1, p_{\ell i}}$ be the random variable, with $X_{ \ell i}= 1$, if  subject $i$ correctly identifies the data plot from lineup $\ell$, and 0 otherwise.
We can model $p_{ \ell i}$ with a logistic regression with subject specific random effects as:
\begin{equation} \label{mixed}
g( p_{\ell i} )= X_{\ell i} B +  Z_{\ell i}  \tau_{\ell i},  
\end{equation}

@@

\begin{tabular}{lp{5.5in}}
$X$  & is a design matrix of covariates corresponding to specifics of lineup $\ell$ and subject $i$. Covariates could include  demographic information of individuals, such as age, gender, education level etc. as well lineup-specific elements, e.g. difficulty level. \\
$B$ & is a vector of parameters for fixed effects.\\
$Z_{\ell i}$ & $1 \le i \le K$, $1 \le \ell \le L$  is a design matrix corresponding to random effects specific to individual $i$ and lineup $\ell$.  \\
$\tau$ & is a vector of independent real-valued random variables $\tau_{\ell i}$,  $\tau  \sim  MVN(0,\sigma_\tau I_{KL \times KL})$. $\tau$ will usually include a component incorporating an individual's ability or skill to evaluate lineups.\\
\end{tabular}

@@

{\bf Presenting lineups for evaluation} Each subject got at least 10 lineups for evaluation. For each combination of sample size ($n$) and error SD ($\sigma$) we define the difficulty of the lineup based on the five slope ($\beta$) parameters we choose as shown in table \ref{tbl:experiment_params}. For the smallest slope parameter the difficulty is 0 and for the largest parameter the difficulty is 4. The 10 lineups are choosen as follows;

@@

\begin{table}[hbtp]
\caption{Number of unique subjects and their total feedbacks after applying five screening process on all three experimental data sets.}
\begin{center}
\begin{tabular}{rrrrr|rrrr|rrrr}
  \hline
Screening &  \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\
 \cline{2-5}  \cline{6-9}   \cline{10-13}
criteria & total & male & female & feedbacks & total & male & female & feedbacks & total & male & female & feedbacks \\ 
  \hline
1 & 520 & 264 & 201 & 4914 & 390 & 203 & 182 & 4603 & 257 & 166 &  84 & 2830 \\ 
  2 & 465 & 264 & 201 & 4624 & 385 & 203 & 182 & 4558 & 250 & 166 &  84 & 2782 \\ 
  3 & 384 & 200 & 165 & 4187 & 384 & 199 & 181 & 4573 & 227 & 147 &  78 & 2648 \\ 
  4 & 318 & 168 & 135 & 3395 & 378 & 195 & 179 & 4492 & 205 & 133 &  72 & 2393 \\ 
  5 & 277 & 139 & 124 & 3008 & 374 & 193 & 177 & 4451 & 112 &  73 &  39 & 1410 \\ 
   \hline
\end{tabular}
\end{center}
\label{tbl:summary}
\end{table}

>>>>

Under the null hypothesis $X \sim Binom_{K, 1/m}$, leading to a power of 
\[
\text{Power}_V(\theta)= 1 - Binom_{K, 11/m} (x_\alpha - 1),
\]
where $x_\alpha$ is defined as in (\ref{dfn:test}), as  $P(X \ge x_{\alpha}) < \alpha$.

@@

Let $X_{\ell i} \sim Binom_{1, p_{\ell i}}$ be the random variable, with $X_{ \ell i}= 1$, if  subject $i$ correctly identifies the data plot from lineup $\ell$, and 0 otherwise.
We can model $p_{ \ell i}$ with a logistic regression with subject specific random effects as:
\begin{equation} \label{mixed}
g( p_{\ell i} )= X_{\ell i} B +  Z_{\ell i}  \tau_{i\ell},  
\end{equation}

@@

\begin{tabular}{lp{5.5in}}
$X$  & is a design matrix of covariates corresponding to specifics of lineup $\ell$ and subject $i$. Covariates could include  demographic information of individuals, such as age, gender, education level etc. as well lineup-specific elements, e.g. difficulty level. \\
$B$ & is a vector of parameters for fixed effects.\\
$Z_{i\ell}$ & $1 \le i \le K$, $1 \le \ell \le L$  is a design matrix corresponding to random effects specific to individual $i$ and lineup $\ell$.  \\
$\tau$ & is a vector of independent real-valued random variables $\tau_{i\ell}$,  $\tau  \sim  MVN(0,\sigma_\tau I_{KL \times KL})$. $\tau$ will usually include a component incorporating an individual's ability or skill to evaluate lineups.\\
\end{tabular}

@@

{\bf Presenting lineups for evaluation} Each subject got at least 10 lineups for evaluation. For each combination of sample size ($n$) and error SD ($\sigma$) we define the difficulty of the lineup based on the five slope ($\beta$) parameters we choose as shown in table \ref{tbl:experiment_params}. For the smallest slope parameter the difficulty is 0 and for the largest parameter the difficulty is 4. The 10 lineups are chosen as follows;

@@

\begin{table}[hbtp]
\caption{Number of participants and their total feedbacks after applying five screening process on all three experimental data sets.}
\begin{center} {\small
\begin{tabular}{rrrrr|rrrr|rrrr}
  \hline 
Screening &  \multicolumn{4}{c} {Experiment 1}  & \multicolumn{4}{c} {Experiment 2}  & \multicolumn{4}{c} {Experiment 3} \\
 \cline{2-5}  \cline{6-9}   \cline{10-13}
criteria & total & male & female & feedbacks & total & male & female & feedbacks & total & male & female & feedbacks \\ 
  \hline
1 & 520 & 264 & 201 & 4914 & 390 & 203 & 182 & 4603 & 257 & 166 &  84 & 2830 \\ 
  2 & 465 & 264 & 201 & 4624 & 385 & 203 & 182 & 4558 & 250 & 166 &  84 & 2782 \\ 
  3 & 384 & 200 & 165 & 4187 & 384 & 199 & 181 & 4573 & 227 & 147 &  78 & 2648 \\ 
  4 & 318 & 168 & 135 & 3395 & 378 & 195 & 179 & 4492 & 205 & 133 &  72 & 2393 \\ 
  5 & 277 & 139 & 124 & 3008 & 374 & 193 & 177 & 4451 & 112 &  73 &  39 & 1410 \\  
   \hline
\end{tabular} }
\end{center}
\label{tbl:summary}
\end{table}
